---
title: "coffee05"
author: "Ben Denis Shaffer"
date: "11/12/2017"
output: html_document
---

```{r}

library(igraph)
library(dplyr)
library(ggplot2)
library(tidyr)
library(GGally)
library(stringr)

coffeeG05 = read_graph("coffeeG05.gml", format = "gml")

```


```{r}
df = data.frame(cl = centr_clo(coffeeG05)$res,
                bt = centr_betw(coffeeG05)$res, 
                dg = degree(coffeeG05),
                indg = degree(coffeeG05, mode = "in"),
                outdg = degree(coffeeG05, mode = "out"),
                country = names(V(coffeeG05)))
```

Countries with the four greatest betweenness centralities are USA, Germany, Italy followed by South Africa. 
In terms of degree centrality the top three are Germnay, Italy and USA respectivly, followed by the EU region and Viet Nam.
Germany, USA, and UK have the greatest incooming edges, followed by Japan and France.
In term of outdegree we have the EU region, Viet Nam, Italy, and then Brazil. It is worth noting that EU-28 region is obviously used as an exporting mechanism since it only has eminating edges and no imports.
Excluding EU-28, Rawanda, Madagascar, Togo, and Viet Nam has the greatest closeness centrality. We can note that the three African countries mentioned all exclusively ecport and don't import.

```{r}

head(df %>% arrange(desc(bt)),10)
head(df %>% arrange(desc(dg)),10)
head(df %>% arrange(desc(indg)),10)
head(df %>% arrange(desc(outdg)),10)
head(df %>% arrange(desc(cl)),10)

```


```{r}

df %>% filter(cl > 0.05, cl < 0.12) %>% select(cl, bt, dg, indg, outdg) %>% ggpairs()

```

```{r}
USAout = E(coffeeG05)[from("USA")]
sub_names = c(str_replace(attributes(USAout)$vnames, "USA\\|", ""),"USA")
USAsub1 = induced_subgraph(coffeeG05, vids = sub_names)

lay3 = layout.kamada.kawai(USAsub1)
plot(USAsub1, vertex.color = betweenness(USAsub1), layout = lay3, 
     vertex.label.cex = 0.5, vertex.size = degree(USAsub1, mode = "in"), 
     edge.arrow.size = 0.2, edge.width = 0.2)

```


```{r}
Rwandaout = E(coffeeG05)[from("Rwanda")]
sub_names = c(str_replace(attributes(Rwandaout)$vnames, "Rwanda\\|", ""),"Rwanda")
Rwandasub1 = induced_subgraph(coffeeG05, vids = sub_names)

lay3 = layout.kamada.kawai(Rwandasub1)
plot(Rwandasub1, vertex.color = betweenness(Rwandasub1), layout = lay3, 
     vertex.label.cex = 0.5, vertex.size = degree(Rwandasub1, mode = "out"), 
     edge.arrow.size = 0.2, edge.width = 0.2)

```




